What do incoming university students believe about open science practices in

### 2021-02-19 analysis/Manuscript.Rmd
stash these

@@

Of those who started the survey (*n* = `r n_all`), we screened out `r ex` 
participants who were not eligible to participate based on the combination of our
preregistered exclusion criteria. Specifically, we screened out people who were younger than 
18 years (*n* = `r age[1,2]`). We also screened out individuals who had already 
started a psychology unit at a university, regardless of whether they had 
completed it (*n* = `r el[1,2] + el[3,2] + el[4,2]`); were not enrolled in a 
psychology unit at a university (*n* = `r el[2,2]`); or did not answer this 
question (*n* = `r el[6,2]`). We also screened out an additional XX participants
who met our eligibility criteria, but did not respond to any of the main items
in the study.

>>>>

nmiss <- df_all %>% 
  dplyr::count(nmiss)

@@

Of those who started the survey (*n* = `r n_all`), we screened out `r ex` 
participants who were not eligible to participate based on the combination of our
preregistered exclusion criteria. Specifically, we screened out people who were younger than 
18 years (*n* = `r age[1,2]`). We also screened out individuals who had already 
started a psychology unit at a university, regardless of whether they had 
completed it (*n* = `r el[1,2] + el[3,2] + el[4,2]`); were not enrolled in a 
psychology unit at a university (*n* = `r el[2,2]`); or did not answer this 
question (*n* = `r el[6,2]`). We also screened out an additional  participants
who met our eligibility criteria, but did not respond to any of the main items
in the study.
